deckard: A Declarative Tool for Machine Learning Robustness Evaluations

### 2025-05-08 paper.tex
typos

The system is compatible with a variety of ML frameworks and several
classes of adversarial attacks, making it a suitable backend for both
large-scale automated testing and fine-grained empirical analysis. By
providing a unified interface for experimental control, \texttt{deckard}
accelerates the development and evaluation of robust models, and helps
close the gap between research prototypes and verifiable, reproducible
results.

@@

Various versions of this software have been used in several recently
published and not-yet-published works by the author of this paper, all
of which are available in the \texttt{examples} folder in the source
code repository \url{https://github.com/simplymathematics/deckard}. One
published work, now reproducible via the
\texttt{examples/attack\_defence\_survey} folder, includes a large
survey of attacks and defences against canonical datasets and models (C.
Meyers, Löfstedt, and Elmroth 2023). Another work analysed the run-time
requirements of attacks against a particular model before and after
retraining against those attacks (Charles Meyers and Elmroth 2024)
(reproducible via \texttt{examples/retraining}). The next paper
formalised a method for estimating the time-to-failure of a given model
against a suite of attacks and introduce a metric that quantifies the
ratio of attack and training cost (Meyers et al. 2023) (reproducible via
\texttt{examples/survival\_heuristic}). Furthemore, a not yet published
work uses this time-to-failure model as a mechanism for analysing the
cost efficacy of various hardware choices in the context of adversarial
attacks (reproducible via \texttt{examples/power}) (C. Meyers et al.
2024). Another work exploits the tooling to train a custom model that is
designed to run client-side by using compression algorithms to measure
the distance between text (reproducible via
\texttt{examples/compression}).

@@

Typically ML projects are composed of long and complex pipelines that
are highly dependent on a number of parameters that must be configured
by either the model builder or attacker. Due to the large scale and cost
associated with training ML models, it is often necessary to tune a
model using many indivudal model configurations (often called
\emph{hyper-paremeters}). To determine adversarial robustness, one of
many benchmark datasets is first sampled, then preprocessed, sent to a
model, with optional pre- and post-processing defences, and then scored
according to some chosen metric which may include the performance
against any number of adversarial attacks. Each stage in this example
pipeline might include tens or hundreds of possible sets of
hyper-parameters that must be exhaustively tested. Furthermore, this
problem scales drastically as we include more and more stages in a
pipeline since each additional stage introduces a new combinatorial
layer of complexity, rapidly expanding the total number of potential
configurations that must be evaluated for robustness and be reproducible
for posterity. Not only does \texttt{deckard} provide a standard way to
document and configure these hyper-parameters, it gives each experiment
an auditable identifier.

@@

Since ML projects can exploit specialized hardware such as multi-core
processors or GPUs, and often rely on clusters of machines for
large-scale data processing, it was necessary to enable parallel and
distributed experiment execution and model optimization. By leveraging
the \texttt{hydra} configuration framework, \texttt{deckard}
automatically supports optimization libraries like \texttt{nevergrad}
(Bennet et al. 2021), \texttt{Adaptive\ Experimentation} (A. Developers
2025), and \texttt{optuna} (Akiba et al. 2019), making the software
modular and extensible. Additionally, experiments can be managed using a
variety of popular job schedulers, including \texttt{Ray} (Moritz et al.
2018), \texttt{Redis\ Queue} (Stamps 2025), and \texttt{slurm} (Yoo,
Jette, and Grondona 2003) for distributd jobs or \texttt{joblib} (J.
Developers 2025) for jobs on a single machine.

>>>>

The system is compatible with a variety of ML frameworks and several
classes of adversarial attacks, making it a suitable back-end for both
large-scale automated testing and fine-grained empirical analysis. By
providing a unified interface for experimental control, \texttt{deckard}
accelerates the development and evaluation of robust models, and helps
close the gap between research prototypes and verifiable, reproducible
results.

@@

Various versions of this software have been used in several recently
published and not-yet-published works by the author of this paper, all
of which are available in the \texttt{examples} folder in the source
code repository \url{https://github.com/simplymathematics/deckard}. One
published work, now reproducible via the
\texttt{examples/attack\_defence\_survey} folder, includes a large
survey of attacks and defences against canonical datasets and models (C.
Meyers, Löfstedt, and Elmroth 2023). Another work analysed the run-time
requirements of attacks against a particular model before and after
retraining against those attacks (Charles Meyers and Elmroth 2024)
(reproducible via \texttt{examples/retraining}). The next paper
formalised a method for estimating the time-to-failure of a given model
against a suite of attacks and introduce a metric that quantifies the
ratio of attack and training cost (Meyers et al. 2023) (reproducible via
\texttt{examples/survival\_heuristic}). Furthermore, a not yet published
work uses this time-to-failure model as a mechanism for analysing the
cost efficacy of various hardware choices in the context of adversarial
attacks (reproducible via \texttt{examples/power}) (C. Meyers et al.
2024). Another work exploits the tooling to train a custom model that is
designed to run client-side by using compression algorithms to measure
the distance between text (reproducible via
\texttt{examples/compression}).

@@

Typically ML projects are composed of long and complex pipelines that
are highly dependent on a number of parameters that must be configured
by either the model builder or attacker. Due to the large scale and cost
associated with training ML models, it is often necessary to tune a
model using many individual model configurations (often called
\emph{hyper-parameters}). To determine adversarial robustness, one of
many benchmark datasets is first sampled, then preprocessed, sent to a
model, with optional pre- and post-processing defences, and then scored
according to some chosen metric which may include the performance
against any number of adversarial attacks. Each stage in this example
pipeline might include tens or hundreds of possible sets of
hyper-parameters that must be exhaustively tested. Furthermore, this
problem scales drastically as we include more and more stages in a
pipeline since each additional stage introduces a new combinatorial
layer of complexity, rapidly expanding the total number of potential
configurations that must be evaluated for robustness and be reproducible
for posterity. Not only does \texttt{deckard} provide a standard way to
document and configure these hyper-parameters, it gives each experiment
an auditable identifier.

@@

Since ML projects can exploit specialized hardware such as multi-core
processors or GPUs, and often rely on clusters of machines for
large-scale data processing, it was necessary to enable parallel and
distributed experiment execution and model optimization. By leveraging
the \texttt{hydra} configuration framework, \texttt{deckard}
automatically supports optimization libraries like \texttt{nevergrad}
(Bennet et al. 2021), \texttt{Adaptive\ Experimentation} (A. Developers
2025), and \texttt{optuna} (Akiba et al. 2019), making the software
modular and extensible. Additionally, experiments can be managed using a
variety of popular job schedulers, including \texttt{Ray} (Moritz et al.
2018), \texttt{Redis\ Queue} (Stamps 2025), and \texttt{slurm} (Yoo,
Jette, and Grondona 2003) for distributd jobs or \texttt{joblib} (Joblib
Developers 2025) for jobs on a single machine.
